Measuring Perceptions and Preferences for Meritocracy

### 2020-12-21 docs/paper.Rmd
save-files

```{r eval=FALSE, include=FALSE}
# for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
# clean #in the yml
rmarkdown::render("docs/paper.Rmd", output_format = "bookdown::pdf_document2")
rmarkdown::render("docs/paper.Rmd", output_format = "bookdown::html_document2")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,out.width = '85%',fig.pos= "H")
# knitr::opts_knit$set(base.url = "../") #relative path for .html output file
# knitr::opts_knit$set(root.dir = "../") #relative path for chunks within .rmd files
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
options(knitr.graphics.error = FALSE)
Sys.setlocale("LC_ALL", "ES_ES.UTF-8")
```

@@

```{r desc01, echo=FALSE}
cap <- "Descriptive statistics of the scale."
load(file = "../input/data/proc/dat04.RData")
dat04b<- dat04 %>% rename("A. Perception Effort" =perc_effort,
 "B. Perception Talent" = perc_talent,
 "C. Perception rich parents" = perc_wpart,
 "D. Perception contacts" = perc_netw,
 "E. Preferences Effort" = pref_effort,
 "F. Preferences Talent" = pref_talent,
 "G. Preferences rich parents" = pref_wpart ,
 "H. Preferences contacts" = pref_netw )
sum04b <- psych::describe(dat04b[,-c(1)], fast = T) %>% select(mean,sd,min,max) %>% data.frame() %>% round(digits = 2)
table04b<- sum04b %>% rename("Mean"=mean, "SD"=sd, "Min"=min,"Max"=max)
sumdat04<- kable(table04b,format =table_format,
                 booktabs= T,
                 #exhaust = FALSE,
                 align = "l",
                 linesep = "",
                 caption = cap) %>%
  kable_styling(full_width = table_format2,
                font_size = 10,
                position = "center",
                latex_options = c("HOLD_position"));sumdat04
```

>>>>

```{r eval=FALSE, include=FALSE}
# for render in pdf run rmarkdown::render_site("docs/paper.Rmd", output_format = "all")
# clean #in the yml
rmarkdown::render("paper.Rmd", output_format = "bookdown::pdf_document2")
rmarkdown::render("paper.Rmd", output_format = "bookdown::html_document2")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,out.width = '85%',fig.pos= "H")
# knitr::opts_knit$set(base.url = NULL) #relative path for .html output file
# knitr::opts_knit$set(root.dir = NULL) #relative path for chunks within .rmd files
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
options(knitr.graphics.error = FALSE)
Sys.setlocale("LC_ALL", "ES_ES.UTF-8")
```

@@

```{r desc01, echo=FALSE}
cap <- "Descriptive statistics of the scale."
load(file = "../input/data/proc/dat04.RData")
dat04b<- dat04 %>% rename("A. Perception Effort" =perc_effort,
 "B. Perception Talent" = perc_talent,
 "C. Perception rich parents" = perc_wpart,
 "D. Perception contacts" = perc_netw,
 "E. Preferences Effort" = pref_effort,
 "F. Preferences Talent" = pref_talent,
 "G. Preferences rich parents" = pref_wpart ,
 "H. Preferences contacts" = pref_netw )
sum04b <- psych::describe(dat04b[,-c(1)], fast = T) %>% 
  as.data.frame() %>%
  select(mean,sd,min,max) %>% 
  round(digits = 2)
table04b<- sum04b %>% rename("Mean"=mean, "SD"=sd, "Min"=min,"Max"=max)
sumdat04<- kable(table04b,format =table_format,
                 booktabs= T,
                 #exhaust = FALSE,
                 align = "l",
                 linesep = "",
                 caption = cap) %>%
  kable_styling(full_width = table_format2,
                font_size = 10,
                position = "center",
                latex_options = c("HOLD_position"));sumdat04
```
